Transparent Changes

### 2022-04-15 transparent_changes.Rmd
Update transparent changes document

@@

#### Unblinding of single abstract

@@

>>>>

## Major Changes

#### Addditional variables extracted from included research

`outcome`: Which type of outcome VO2max is. Either `primary`, `secondary` or `other`
`source`: Which source is provided for the data processing method used.

@@

#### Unblinding of single abstracts

@@

#### Minor Modification of exclusion criteria

Changes are in italics:

`'r'`: Is the article no original research *(i.e. no primary analysis of experimental data)* ? (if yes, indicate 'r'; if no, continue)

`'t'`: Was no full-text ~~available~~ *accessible* for the corresponding article? (if yes, indicate 't', if no continue)
